---
title: "Your Title Here"
author: "Don Francisco"
date: "August 27, 2019"
output:
  word_document: default
  pdf_document: default
csl: bioinformatics.csl
bibliography: references.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

# Introduction

# Methods

## Study design

## Analysis

# Results

```{r load-libraries}
library("ggplot2")
library("dplyr")
library("tidyr")
library("readr")
library("broom")
library("knitr")
```

```{r read-in-culture-data}
# read in the culture data from csv
culture_data <- read_csv(
  "data/raw_data/raw_culture_count_data/BIOL422_culturing_data.csv")
```

```{r filter-and-plot-abundances}
# filter out only my 100x dilutions and make a boxplot
culture_data %>%
  filter(student_name == "Adelle Sumabat") %>%
  filter(dilution_1_10_or_100 == "10") %>%
  ggplot(aes(x = sample_group,
             y = number_of_colonies)) +
  geom_boxplot() +
  ggtitle("Comparison of colony abundances between Personal Bathrooms",
                "and Public Restrooms, 10x dilution") +
  xlab("Sample Group") +
  ylab("Number of Colonies")
```

**Figure 1:** Boxplot of colony abundances at different sites, 10x dilution. Despite a higher median number of colonies from Personal Bathroom samples, the mean numbers of colonies were not significantly different between the two sites. (Wilcox p = 0.35).

```{r abundances-stats}
# run a statistical test to compare the two groups of abundances
culture_data %>%
  filter(student_name == "Adelle Sumabat") %>%
  filter(dilution_1_10_or_100 == "10") %>%
  wilcox.test(data = .,
              number_of_colonies ~ sample_group) %>%
  broom::glance(x = .) %>%
  knitr::kable()
```

```{r filter-and-plot-morphotypes}
# filter out only my 100x dilutions and make a boxplot
culture_data %>%
  filter(student_name == "Adelle Sumabat") %>%
  filter(dilution_1_10_or_100 == "100") %>%
  ggplot(aes(x = sample_group,
             y = as.numeric(number_of_morphotypes))) +
  geom_boxplot() +
  ggtitle("Comparison of morphotypes between Personal Bathrooms",
                "and Public Restrooms, 100x dilution") +
  xlab("Sample Group") +
  ylab("Number of Morphotypes")
```

**Figure 2:** Boxplot showing the number of morphotypes from the two different sites, 100x dilution. There was no difference in the mean number of morphotypes (Wilcox p=0.1).

```{r morphotypes-stats}
# run a statistical test to compare the two groups of abundances
culture_data %>%
  filter(student_name == "Adelle Sumabat") %>%
  filter(dilution_1_10_or_100 == "100") %>%
  wilcox.test(data = .,
              as.numeric(number_of_morphotypes) ~ sample_group) %>%
  broom::glance(x = .) %>%
  knitr::kable()
```




## Subsections are ok in the results section too

```{r your-code-here}
# Add code chunks as needed for your analyses
```

# Discussion

# Sources Cited
